Laws for Creating Trust in the Blockchain Age

### 2017-07-25 tex/article.tex
Splitting IoM and conditional payments
Polished abstract

  \author*[1]{Johan Pouwelse}
  \author[2]{Martijn de Vos}
  \runningauthor{Johan Pouwelse and Martijn de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{Department of Software Technology, Delft University of Technology}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour and creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, they are often facilitated by a few predatory companies. This centralization of power raises questions about ethical and political issues like regulatory compliance, data portability (lock-in) and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of public support, due to its inherent decentralized and tamper-proof nature.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

@@

>>>>

  \author*[1]{Johan Pouwelse}
  \author[2]{Martijn de Vos}
  \runningauthor{Johan Pouwelse and Martijn de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{Department of Software Technology, Delft University of Technology}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond what's possible in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

@@

\subsection{Conditional Payments and Smart Contracts}
\label{sec:smart_contracts}
